Current State of Knowledge Representation Systems for Robotics

### 2011-12-08 krs-survey.tex
Added a short 'article overview'

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compared Features}
\label{sect|compared-features}

>>>>

\subsection{Article overview}
\label{sect|overview}

The paper is organized in four main sections.

The next section proposes a prototypical scenario in a rich semantic
environment. We will not survey knowledge representation systems based on this
scenario: we merely use it to ground the selection and illustrate the set
features (Section~\ref{sect|features}) that define the dimensions of a
knowledge representation system for robotics.

Section~\ref{sect|surveyed-systems} then presents each of the systems we
examinated, and underlines their specificities.

We try in section~\ref{sect|summary} to summarize the current approaches and to
relate them to the previously identified set of features. This leads us to
identify several new research directions that are not sufficiently addressed by
the current state of the art.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Cognitive Scenario}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compared Features}
\label{sect|features}
